
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}


\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Harsh Deep Rao} \\ 
     Sector-Q, Aliganj, Lucknow \\ 
    \small \href{tel:+917233811034}{ \raisebox{-0.1\height}\faPhone\ \underline{+91-72338 11034} ~} \href{mailto:harshurao058@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{harshurao058@gmail.com}} ~ 
    \href{https://my-portfolio-2026-nu.vercel.app/}{\raisebox{-0.2\height}\faGlobe\ \underline{Portfolio}} ~
    \href{https://www.linkedin.com/in/harsh-d-rao/}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{Linkedin}}  ~
    \href{https://github.com/harshrao26}{\raisebox{-0.2\height}\faGithub\ \underline{Github}}
\end{center}
\vspace{-18pt}


%-----------SUMMARY-----------
\section*{SUMMARY}
\small{Full Stack Developer with 2+ years of experience building high-performance Next.js applications, scalable APIs, and SEO-optimized web platforms. Strong focus on performance engineering, system integration, and production reliability.}





%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
\vspace{-2pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Languages:}}{ \normalsize{JavaScript (ES6+), TypeScript, Python}} \\
     \textbf{\normalsize{Technologies \& Frameworks:}}{ \normalsize{Next.js 15, React 19, Node.js, Express.js, MongoDB, Postman, Tailwind CSS, Cloudinary}} \\
     \textbf{\normalsize{Web Performance \& SEO:}}{ \normalsize{Technical SEO, Schema Markup (JSON-LD), Core Web Vitals (LCP, CLS, INP), Lighthouse Optimization}} \\
     \textbf{\normalsize{DevOps \& Tools:}}{ \normalsize{DigitalOcean, Nginx, PM2, Docker, Git, Google API, SMTP}} \\
    }}
 \end{itemize}
 \vspace{-8pt}

    
  


%-----------PROJECTS-----------
\section{PROJECTS}
\vspace{-5pt}
\resumeSubHeadingListStart
\vspace{-5pt}

\resumeProjectHeading
{\href{https://onlineplanet.in/}{\textbf{\large{\underline{Online Planet (Multi-Utility Commerce Platform)}}} \href{https://onlineplanet.in/}{\raisebox{-0.2\height}\faExternalLink }} $|$ \large{\underline{Next.js 15, MongoDB, Gemini AI, Tailwind CSS}}}\\
\vspace{-15pt}


\resumeItemListStart
\resumeItem{\normalsize{Architected a high-performance marketplace with 140+ API endpoints and a 12-stage automated order lifecycle, significantly reducing server resource consumption through optimized data structures.}}
\resumeItem{\normalsize{Engineered a deep logistics integration layer with Shiprocket and Ekart, implementing rule-based carrier selection logic to automate status tracking across 15+ checkpoints.}}
\resumeItem{\normalsize{Integrated Google Gemini AI for automated SEO optimization and metadata generation; built an OCR-based verification system to streamline seller onboarding.}}
\resumeItem{\normalsize{Developed an internal advertising network with real-time bidding and ROAS tracking, alongside an automated financial suite for payout reconciliation.}}
\resumeItemListEnd 
\vspace{-11pt}


\resumeProjectHeading
{\href{https://strucaxis.com/}{\textbf{\large{\underline{StrucAxis (Marketing \& Admin Platform)}}} \href{https://strucaxis.com/}{\raisebox{-0.2\height}\faExternalLink }} $|$ \large{\underline{Next.js, MongoDB, Cloudinary, Google API}}}\\
\vspace{-15pt}
\resumeItemListStart
\resumeItem{\normalsize{Developed a custom Blog CMS and content management platform with secure role-based access control and advanced SEO metadata management.}}
\resumeItem{\normalsize{Built automated career and project tracking modules with display priority logic and Cloudinary-based media management.}}
\resumeItem{\normalsize{Implemented a contact pipeline that synchronizes inquiries with Google Sheets via API and triggers SMTP-based email alerts.}}
\resumeItemListEnd
\vspace{-11pt}


\resumeProjectHeading
{\href{https://naturemedica.in/}{\textbf{\large{\underline{Nature Medica (Ayurvedic E-Commerce)}}} \href{https://naturemedica.in/}{\raisebox{-0.2\height}\faExternalLink }} $|$ \large{\underline{Next.js 15, MongoDB, Redux Toolkit, Tailwind CSS v4}}}\\
\vspace{-15pt}


\resumeItemListStart
\resumeItem{\normalsize{Architected a premium Ayurvedic storefront with Next.js 15 and Turbopack, optimizing for sub-2s initial load times and high Core Web Vitals.}}
\resumeItem{\normalsize{Engineered a tri-integrated logistics engine (Shiprocket, Delhivery, Ekart) with automated AWB generation to streamline fulfillment.}}
\resumeItem{\normalsize{Built a redundant payment ecosystem with recovery logic for abandoned transactions and partial COD flows to reduce RTO losses.}}
\resumeItem{\normalsize{Integrated a GA4 DataLayer analysis engine for granular funnel tracking and predictive search intent optimization.}}
\resumeItemListEnd 
\resumeSubHeadingListEnd
\vspace{-15pt}

     
 


\section{EXPERIENCE / INTERNSHIP}
  \resumeSubHeadingListStart

    

  \resumeSubHeadingListStart

\resumeSubheading
  {Lawfinity India PVT. LTD.}{June 2025 - Present}
  {Full Stack Developer (Full Time)}{Lucknow, India}
 
  \resumeItemListStart
\resumeItem{\normalsize{Own development and maintenance of high-performance enterprise applications using Next.js 15, TypeScript, and Tailwind CSS.}}

\resumeItem{\normalsize{Architect reusable UI systems and optimize server-side rendering, routing, and server actions for scalability.}}
\resumeItem{\normalsize{Design and integrate secure backend APIs using Node.js and MongoDB with JWT-based authentication.}}
\resumeItem{\normalsize{Lead performance engineering efforts to improve SEO, Lighthouse metrics, and Core Web Vitals (LCP, CLS, INP).}}
\resumeItem{\normalsize{Manage production deployments on DigitalOcean, configuring Nginx, PM2, and automated CI/CD workflows.}}
  
  \resumeItemListEnd

 

\resumeSubheading
  {Propques Services PVT. LTD.}{Oct 2024 - June 2025}
  {Full Stack Developer }{Full Time}
 
  \resumeItemListStart
  
\resumeItem{\normalsize{The company website, \href{https://propques.com/}{\textbf{{Propques.com}}}, was revamped, leading to a 40\% improvement in load time and a 25\% increase in user engagement.}}

    \resumeItem{\normalsize {APIs were developed and integrated using \textbf{Make}, resulting in a 30\% reduction in data processing time.}}
    \resumeItem{\normalsize{\textbf{EmailJS} was implemented for efficient email handling, and \textbf{Otpless} was utilized for secure authentication, improving user login success rates by 20\%.}}
    \resumeItem{\normalsize{Front-end designs were enhanced using \textbf{Predis.ai} and \textbf{Photoshop}, leading to a 35\% increase in user satisfaction based on surveys.}}
  
  \resumeItemListEnd

   

  
    \resumeSubheading
      {{UnBoxing Community} }{2 Months } 
      {{React Developer }}{Intern}
      % {\underline{React Developer Intern}}{Virtual}
      \resumeItemListStart

 
      
\resumeItem{\normalsize{Integrate frontend components with backend services, working closely with the backend team to ensure seamless data flow and functionality. 
}}
\resumeItem{\normalsize{Collaborate with the design team to translate UI/UX wireframes into high-quality code, creating user-friendly and visually appealing components.
}}

\resumeItemListEnd 
 
 

\resumeSubheading
      {Adi Laxmi Exports }{1 Month} 
      {{Full Stack Developer }}{Intern}
      \resumeItemListStart
 
      
\resumeItem{\normalsize{Application performance and scalability were prioritized, leading to a 25\% reduction in page load times across all platforms. }}


\resumeItem{\normalsize{Interactive user interfaces were created and optimized using React.js, resulting in a 30\% improvement in user engagement metrics.
}}

\resumeItemListEnd 
\resumeSubHeadingListEnd
\resumeSubHeadingListEnd
 

  %-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bansal Institute of Engineering and Technology}{2020 – 2024}
      {B.Tech - Computer Science and Engineering}{Lucknow, Uttar Pradesh}
  \resumeSubHeadingListEnd


 
 
 \end{document}
 
